\showyourwork: a workflow for open source scientific articles

### 2021-12-17 src/ms.tex
tweaks

% Title
\title{\texttt{showyourwork}: a workflow for open source scientific articles}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{static/eclipse.jpeg}
        \caption{
            A static figure committed to the repository showing a total solar eclipse. 
            Since this figure is in the \texttt{src/static} directory, \showyourwork knows not to attempt to generate it. 
            By default, margin icons are not added to static figures.
            Here we manually add icons linking to the original photograph and its license using the \texttt{\textbackslash marginicon} command.
        }
        \marginicon{%
            \stackon[3pt]{%
                \href{https://commons.wikimedia.org/wiki/File:Total\_Solar\_Eclipse\_8-21-17.jpg}{\color{sywBlue}\faWikipediaW}%
            }{%
                \href{https://commons.wikimedia.org/wiki/File:Total\_Solar\_Eclipse\_8-21-17.jpg\#Licensing}{\color{sywBlue}\faCreativeCommons}%
            }%
        }
        \label{fig:eclipse}
    \end{centering}
\end{figure}

>>>>

% Title
\title{\showyourwork: a workflow for open source scientific articles}

@@

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.75\linewidth]{static/eclipse.jpeg}
        \caption{
            A static figure committed to the repository showing a total solar eclipse. 
            Since this figure is in the \texttt{src/static} directory, \showyourwork knows not to attempt to generate it. 
            By default, margin icons are not added to static figures.
            Here we manually add icons linking to the original photograph on Wikimedia Commons and its license using the \texttt{\textbackslash marginicon} command.
        }
        \marginicon{%
            \stackon[3pt]{%
                \href{https://commons.wikimedia.org/wiki/File:Total\_Solar\_Eclipse\_8-21-17.jpg}{\color{sywBlue}\faWikipediaW}%
            }{%
                \href{https://commons.wikimedia.org/wiki/File:Total\_Solar\_Eclipse\_8-21-17.jpg\#Licensing}{\color{sywBlue}\faCreativeCommons}%
            }%
        }
        \label{fig:eclipse}
    \end{centering}
\end{figure}
